### 2010-12-10 Text/paper.tex
Modified code and compare.py - the machine accurate results. Really strange.

>>>>

\citet{cerro-bubble-train} performed a lot of experiments for a buble-train flow in capillaries of
circular and square cross section for horizontal, upward and downward flows. The main results are
presented in Fig. \ref{fig:thulasidas:results}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/thulasidas_capillary.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/thulasidas_relative_velocity.eps}\\
\caption{\citet{cerro-bubble-train} results for the film thickness
variation and the relative bubble velocity versus the capillary
number.\label{fig:thulasidas:results}}
\end{figure}

\citet{wang-non-circular} performed numerical simulations by VOF technique to for the non-circular
shaped capillaries as square and triangle shaped capillaries. Some interesting results for bubble
shape depending on the capillary number, Fig. \ref{fig:wang:bubble:shape}. They also included
numerical simulations for the determination of the critical capillary number $\hat{Ca}$, Fig.
\ref{fig:wang:critical:capillary}. 
\begin{figure}
\includegraphics[width=\textwidth]{Figures/wang_bubble_shape.eps}
\caption{The bubble shape across the length for different capillary numbers.
\label{fig:wong:bubble:shape}}
\end{figure}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/wang_critical_capillary.eps}\hfill
\caption{Bubble radiuses variations over the range of capillary numbers (left) and the relative
velocity for th  \label{fig:wang:critical:capillary}}
\end{figure}
